---
output: github_document
title:  Exploring Parameters
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
Parameters can be explored in the model. There are a number of categories, see below for their descriptions, and default values. These can be set and retrieved using the functions **set_params(mod,param,value)** and **get_params(mod,param)**

* First, load in the libraries

```{r,message=F}
library(seirR)
library(dplyr)
```

* Next, call the constructor to create an S3 model object

```{r}
mod <- create_seir_p()
```

* **(1) Initial conditions**


```{r}
mod$params %>% filter(ParameterType=="InitialCondition") %>% select(ParameterName,Value,Description)
```

* **(2) Transmission**
```{r}
mod$params %>% filter(ParameterType=="Transmission") %>% select(ParameterName,Value,Description)
```

* **(3) Biological**
```{r}
mod$params %>% filter(ParameterType=="Biological") %>% select(ParameterName,Value,Description)
```

* **(4) Pathway**
```{r}
mod$params %>% filter(ParameterType=="Pathway") %>% select(ParameterName,Value,Description)
```

* **(5) Distancing**
```{r}
mod$params %>% filter(ParameterType=="Distancing") %>% select(ParameterName,Value,Description)
```

* **(6) Health System**
```{r}
mod$params %>% filter(ParameterType=="HealthSystem") %>% select(ParameterName,Value,Description)
```

* **(7) Health System**
```{r}
mod$params %>% filter(ParameterType=="Pulse") %>% select(ParameterName,Value,Description)
```

* **(8) Model**
```{r}
mod$params %>% filter(ParameterType=="Model") %>% select(ParameterName,Value,Description)
```
