---
output: github_document
title:  Running a model
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
In order to run a model, the following steps should be taken.

* First, load in the libraries, and include **ggplot2** for visualisation

```{r}
library(seirR)
library(ggplot2)
library(dplyr)
```

* Next, call the constructor to create an S3 model object

```{r}
mod <- create_seir_p()
```

The **mod** variable has the following S3 structure.
```{r}
class(mod) 
```

The **mod** variable has three list elements, as follows:
```{r}
str(mod) 
```

The first is a tibble with the parameters for the simulation run.
```{r}
mod$params
```

The second will contain information on pulse policies that can be activated/deactivated.
```{r}
mod$pulse
```

The third contains a mapping from the simulation time to the calendar date
```{r}
mod$sim_date
```

The third contains a mapping fof contacts based on the polymod study
```{r}
mod$POLYMOD
```


* A model can then be run based on the **mod** object by calling the function **run()** In this example, we run the model twice, and alter a parmeter using the **set_params()** function

```{r}
out1 <- run(mod)
mod <- set_param(mod,"distancing_flag",1)
out2 <- run(mod)
```

The output from these models is a tibble, containing a good deal of simulation information.
```{r}
glimpse(out1)
```

Any of these variables can then be printed.
```{r}
ggplot()+geom_line(out1,mapping=aes(x=SimDay,y=ReportedIncidence),colour="red")+
  geom_line(out2,mapping=aes(x=SimDay,y=ReportedIncidence),colour="blue")
```

