---
output: github_document
title:  Running a model
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
In order to run a model, the following steps should be taken.

* First, load in the libraries, and include **ggplot2** for visualisation

```{r}
library(seirR)
library(ggplot2)
library(dplyr)
library(readsdr)
```

* Next, call the constructor to create an S3 model object

```{r}
mod <- create_seir_p()
```

The **mod** variable has the following S3 structure.
```{r}
class(mod) 
```

The **mod** variable has a number of  list elements, as follows:
```{r}
str(mod) 
```

The paramters that drive the model can be viewed using the **summary** function. Note that there are escape characters in the output in order that the descriptions are shown in red when used at the console.
```{r}
summary(mod) 
```


* A model can then be run based on the **mod** object by calling the function **run()** In this example, we run the model twice, and alter a parmeter using the **set_params()** function


```{r}
mod <- create_seir_p()
out1 <- run(mod)
ggplot()+geom_line(out1,mapping=aes(x=SimDay,y=Reported_Incidence),colour="red")
```


The output from these models is a tibble, containing a good deal of simulation information.
```{r}
glimpse(out1)
```

The behaviour modes of variables can be explored by calling the function **get_curve_analysis()**. The descriptors here include:

- INC-INC (increasing at an increasing rate)
- INC-DEC (increating at a decreasing rate)
- DEC-INC (decreasing at an increasing rate)
- DEC-DEC (decreasing at a decreasing rate)
```{r}
vars <- c("Reported_Incidence")

ca <- get_curve_analysis(out1,vars)

ggplot(ca,aes(x=SimDay,y=Value,colour=Behaviour))+geom_point()+facet_grid(Variable~.)
```

