---
output: github_document
title:  Sensitivity Analysis
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
Sensitivity analysis runs can be  performed. 

* First, packages are loaded including **purrr**, **dplyr** and **ggplot2**

```{r,message=F}
library(seirR)
library(ggplot2)
library(purrr)
library(dplyr)
library(readsdr)
```


* Next, the model is created with the distancing on, and to be continued until time 300.

```{r}
mod <- create_seir_p()
mod <- set_param(mod,"Distancing_Switch",1)
mod <- set_param(mod,"Switch_Time",300) # time to end continuous physcial distancing
```


* Setup for 20 runs, varying two parameters.

```{r}
NRUNS <- 10

lower <- 0.2
upper <- 0.8
percentages    <- runif(NRUNS,.1,.9)
f_asymptomatic <- runif(NRUNS,.15,.7)
```

* Use purrr function **map_df()** to control the sensitivity process

```{r}
res_full <- map_df(1:NRUNS, function(i){
  cat("iteration = ", i, "with percentage = ", percentages[i], " and f = ",f_asymptomatic[i],"\n")
  mod <- set_param(mod,"Percentage_Reduction_of_Physical_Disancing",percentages[i])
  mod <- set_param(mod,"Proportion_Asymptomatic_f",f_asymptomatic[i])
  out2 <- run(mod) %>% mutate(RunNumber=i) %>%
     select(RunNumber,everything())
})
```

* Display the results

```{r}
ggplot(res_full,aes(x=SimDay,y=Reported_Incidence,colour=RunNumber,group=RunNumber))+geom_path()+
       scale_colour_gradientn(colours=rainbow(12))+guides(color=FALSE)
```

* Sample analysis (thanks to Chris Brunsdon (NUIM) for the code)
```{r}
res_peaking <- res_full %>%
  group_by(RunNumber) %>%
  summarise(Peak_RI=max(Reported_Incidence),
            Peak_Time=which.max(Reported_Incidence))
```

* Plot the results
```{r}
ggplot(res_peaking %>% filter(Peak_RI>400),
       aes(x=Peak_Time,y=Peak_RI)) +
  geom_point() + geom_density_2d()
```


