---
output: github_document
title:  Exploring data
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
The package downloads up-to-date COVID-19 numbers from the https://covid.ourworldindata.org/data/ecdc/full_data.csv. 

This data is stored in the **date_env** environment, and can be accessed. The following is the process for doing this

* First, load in the libraries, and include **ggplot2** for visualisation, and **dplyr** and **tidyr** for data manipulation.

```{r, message=F}
library(seirR)
library(ggplot2)
library(dplyr)
library(tidyr)
```

* Explore the data contained in the R environment data_env

```{r}
data_env$covid_data
```

* Filter out a country of interest, and reshape to tidy data format

```{r}
countries <- c("Norway")

ds <- filter(data_env$covid_data,
             Country %in% countries)

ds_piv <- ds %>% pivot_longer(-c(Date,Country),names_to ="Measure",values_to = "Number") %>%
   filter(Measure %in% c("ReportedNewCases","ReportedNewDeaths"))
```

* Explore the re-shaped dataset
```{r}
ds_piv
```

* Visualise some of the results

```{r}
ggplot(ds_piv,aes(x=Date,y=Number,colour=Measure))+
  facet_grid(Measure~.,scales = "free_y")+
  geom_point()+geom_line()+ggtitle("Norway Data")
```

